\Large \bf SIRIUS: A Revolutionary Approach to I/O and Storage for Exascale Scientific Computing

### 2016-03-11 papers/2016-HotStorage/paper.tex
fixed typos

A similar approach that maintains full data quality is to use a data stride to
store only a data subset. For example, by selecting every fourth element in
three dimensions yields a $\frac{1}{64}$ sized data set to store in fast
storage--a mere 1.5\% of the original size. The rest can be spooled
asynchronously. Combining byte-splits and striding can reduce the data sizes
even more. Doing a 3/5 split and an every fourth element yields 0.9\% of the
original size.

@@

The metadata system has a daunting challenge. Traditional metadata systems for
both distributed and parallel file systems only have to deal with a single name
space and storage tier. While hierarichal storage
management~\cite{blaze:1992:hsm} systems offer a way to show a single name
space, the reality is that the tier closest to the user is a cache for the
other tiers with data migrating as necessary to support user interaction.
SIRIUS is working in a fundamentally different way. Each tier is treated as a
first class citizen with direct client access possible. Where data is actually
retrieved from is where it is actually stored rather than forcing data
migration and caching. Systems like Sirocco~\cite{curry:2015:sirocco} offer a
way to support this model directly and are a fundamental part of our system.

>>>>

A similar approach that maintains full data quality is to use a data stride to
store only a data subset. For example, by selecting every fourth element in
three dimensions yields a $\frac{1}{64}$ sized data set to store in fast
storage--a mere 1.5\% of the original size. The rest can be spooled
asynchronously. Combining byte-splits and striding can reduce the data sizes
even more. Doing a 3/5 split and an every fourth element yields 0.5\% of the
original size.

@@

The metadata system has a daunting challenge. Traditional metadata systems for
both distributed and parallel file systems only have to deal with a single name
space and storage tier. While hierarchical storage
management~\cite{blaze:1992:hsm} systems offer a way to show a single name
space, the reality is that the tier closest to the user is a cache for the
other tiers with data migrating as necessary to support user interaction.
SIRIUS is working in a fundamentally different way. Each tier is treated as a
first class citizen with direct client access possible. Where data is actually
retrieved from is where it is actually stored rather than forcing data
migration and caching. Systems like Sirocco~\cite{curry:2015:sirocco} offer a
way to support this model directly and are a fundamental part of our system.
